Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-31 manuscript/manuscript.tex
[manuscript] large system section, incorporate review + major improvement

\subsection{Markov models of large systems}
For modeling large systems, challenges may arise that are mostly system dependent. 
For example, one of them is that finding a state space discretization using e.g.~ $k$-means becomes difficult in very high dimensional spaces. 
It is thus important to choose a feature space and coordinate transformion that yield a low dimensional representation of the slow processes.
Hidden Markov models might further help to overcome poor discretization to a certain extend \cite{noe-proj-hid-msm}.

In addition, the slowest process in a system as identified by a Markov model might not be the one a modeler is interested in. 
For instance, there might be a side chain flip that only occurred once in a data set but has no biological relevance. 
This problem can often be mitigated by choosing a more specific set of features.

Further, large systems come with technical challenges such as huge memory requirements.
We explain how to deal with those in the tutorials. 
More details on how to model complex systems with the techniques presented here are described by e.g. ~\cite{plattner_protein_2015,plattner_complete_2017}.

>>>>

\subsection{Modeling large systems}
When estimating MSMs for large systems, challenges may arise that are mostly system dependent.

A case in point is the curse of dimensionality:
it is hard to discretize a high dimensional feature space, not only because it is computationally demanding.
More important, Euclidean distances become less meaningful with increasing dimensionality~\cite{aggarwal_surprising_2001} and, thus, cluster assignment based on that norm are prone to yield poor discretizations.
Especially for large systems, it is thus particularly important for first find a suitable set of features, and to further apply dimension reduction techniques (e.g. TICA, VAMP, if applicable) to obtain a low-dimensional representation of the slow dynamics.
Hidden Markov models might further mitigate poor discretization to a certain extend~\cite{noe-proj-hid-msm}.

In addition, the slowest process in a system as identified by an MSM or HMM might not be the one a modeler is interested in.
For instance, the slowest process might correspond to a biologically irrelevant side chain flip that only occurred once in the data set.
This problem can often be mitigated by choosing a more specific set of features.

The technical challenges with large systems are usually high demands in memory and computation time; we explain how to deal with those in the tutorials.

More details on how to model complex systems with the techniques presented here are described e.g. by~\cite{plattner_protein_2015,plattner_complete_2017}.
